### 2019-03-27 _publications/jors/paper.tex
Update reuse potential section
More cleanup

The website infrastructure can be cloned as a Git repository or
downloaded as a ZIP archive and deployed with minimum effort. The
mechanism for uploading data using Staticman can be easily configured
for a new repository location. However, customizing the content of the
website for a particular scientific community would require
considerable effort. The following steps are the more challenging
aspects of deploying the framework for a new community.

\begin{itemize}
  \item Upload new data upload specficiations (e.g. the phase-field
    benchmarks in the PFHub website~\cite{pfhub}) in a format that
    Jekyll can parse, \emph{e.g.}, Jupyter Notebook, Markdown or HTML.
  \item Edit the \texttt{benchmarks.yaml} file to reflect the new
    upload requirements and describe the figures that need to be
    generated on the upload comparison pages.
  \item Edit the \texttt{\_config.yml} file to update links and text
    related to the configuration for all aspects of the website.
  \item Update Markdown files to reflect the new content and mission
    of the scientific community.
  \item Remove data and files that are not required by the new
    community.
\end{itemize}

>>>>

The PFHub framework can be readily adopted by other communities that
want to follow a CMS-free philosophy and use well supported external
services. The website infrastructure can be cloned as a Git repository
or downloaded as a ZIP archive and deployed with minimum effort. The
mechanism for uploading data using Staticman can be easily configured
for a new repository location. However, customizing the content of the
website for a particular scientific community would require
considerable effort. The following steps are the more challenging
aspects of deploying the framework for a new community.

\begin{itemize}
  \item Upload new data upload specifications (\emph{e.g.} the
    phase-field benchmarks in the PFHub website~\cite{pfhub}) in a
    format that Jekyll can parse, \emph{e.g.}, Jupyter Notebook,
    Markdown or HTML.
  \item Edit the \texttt{benchmarks.yaml} file to reflect the new
    upload requirements and describe the figures that need to be
    generated on the upload comparison pages.
  \item Edit the \texttt{\_config.yml} file to update links and text
    related to the configuration for all aspects of the website.
  \item Update Markdown files to reflect the new content and mission
    of the scientific community.
  \item Remove data and files that are not required by the new
    community.
\end{itemize}
